\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% Customize hyperlink appearance
\definecolor{darkblue}{RGB}{0,0,120}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% No paragraph indentation
\setlength{\parindent}{0pt}
% \setlength{\parskip}{0.5em} % Optional: adds space between paragraphs

% Section formatting
\titleformat{\section}
    {\normalsize\bfseries\uppercase}
    {}{0em}{}[\titlerule]
\titlespacing*{\section}
    {0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}

% Custom commands for better spacing
\newcommand{\spaced}[1]{\vspace{0.3em}#1\vspace{0.3em}}

\begin{document}

% Header
\begin{center}
    {\Large\bfseries{Geppetto}}\\[0.2em]
    {\normalsize
        \href{mailto:geppetto@woodmail.it}{geppetto@woodmail.it} ~|~
        \href{tel:+39 123 456 7890}{+39 123 456 7890} ~|~
        \href{https://github.com/geppetto-works}{GitHub}
    }
\end{center}

\vspace{0.5em}

% Summary

\section*{Summary}

Master woodcarver with expertise in traditional handcrafted toy design and storytelling. Skilled in mentoring and preserving traditional woodworking techniques.



% Experience
\section*{Experience}

\textbf{Geppetto's Workshop}, \hfill Villaggio Incantato, Italy \\
\textit{Master Woodcarver and Toymaker}, \hfill January 1850 -- Present
\begin{itemize}[leftmargin=*, noitemsep, topsep=0.1em]

    \item Designed and handcrafted over 300 wooden toys including puppets and musical automata, focusing on durability and artistic expression.

    \item Mentored 15 apprentices in traditional woodcarving techniques and shop safety.

    \item Developed innovative joint mechanisms for enhanced puppet mobility and expression.

\end{itemize}
\vspace{0.3em}

\textbf{Puppet Theater of Tuscany}, \hfill Tuscany, Italy \\
\textit{Set Designer and Puppet Articulator}, \hfill June 1848 -- December 1849
\begin{itemize}[leftmargin=*, noitemsep, topsep=0.1em]

    \item Designed stage mechanisms and built expressive puppets for traveling shows.

    \item Worked with performers to enhance articulation through mechanical design.

\end{itemize}
\vspace{0.3em}


% Projects
\section*{Projects}

\textbf{\href{https://en.wikipedia.org/wiki/Pinocchio}{Pinocchio}}, \hfill Ongoing \\
A fully articulated wooden puppet designed for emotional expressiveness. Combines handcrafted form with behavioral systems. \\
\vspace{0.3em}

\textbf{\href{}{Whistle-toy Orchestra}}, \hfill March 1885 \\
A set of carved whistle-operated instruments teaching musical structure through playful experimentation. \\
\vspace{0.3em}


% Education
\section*{Education}

\textbf{Guild of Master Carvers, } \hfill Florence, Italy \\
Journeyman Woodworker Certification, \hfill 1842
\vspace{0.3em}

\textbf{Independent Study, } \hfill Venice, Italy \\
Apprenticeship in Automata Construction and Puppet Mechanics, \hfill 1845
\vspace{0.3em}


% Honors and Awards
\section*{Honors and Awards}

\textbf{Best Toymaker in Tuscany,} \hfill December 1883 \\
Awarded by the Tuscany Chamber of Artisans for craftsmanship, community impact, and imaginative design.
\vspace{0.3em}

\textbf{Patron of the Children's Guild,} \hfill June 1886 \\
Recognized for mentorship and generosity supporting village youth creative expression.
\vspace{0.3em}


% Publications
\section*{Publications}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0.1em]

    \item \textit{\href{}{Toymaking for the Soul: A Handbook for Village Craft Educators}}, with Silvino Boccadutti. Community Education Manual.

    \item \textit{\href{}{On the Practical Construction of Puppet Joints}}. Instructional Manual.

\end{itemize}

\end{document}