\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% Customize hyperlink appearance
\definecolor{darkblue}{RGB}{0,0,120}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% No paragraph indentation
\setlength{\parindent}{0pt}
% \setlength{\parskip}{0.5em} % Optional: adds space between paragraphs

% Section formatting
\titleformat{\section}
    {\normalsize\bfseries\uppercase}
    {}{0em}{}[\titlerule]
\titlespacing*{\section}
    {0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}

% Custom commands for better spacing
\newcommand{\spaced}[1]{\vspace{0.3em}#1\vspace{0.3em}}

\begin{document}

% Header
\begin{center}
    {\Large\bfseries{Geppetto}}\\[0.2em]
    {\normalsize
        \href{mailto:geppetto@woodmail.it}{geppetto@woodmail.it} ~|~
        \href{tel:+39 123 456 7890}{+39 123 456 7890} ~|~
        \href{https://github.com/geppetto-works}{GitHub}
    }
\end{center}

\vspace{0.5em}

% Summary

\section*{Summary}

Artisan and self-taught roboticist with experience designing emotionally expressive wooden constructs.
Passionate about human-centered mechanics and narrative-driven autonomy.
Seeking a role that values ethical robotics, hands-on design, and whimsical engineering.




% Experience
\section*{Experience}

\textbf{Geppetto's Workshop}, \hfill Villaggio Incantato, Italy \\
\textit{Master Woodcarver and Toymaker}, \hfill January 1850 -- Present
\begin{itemize}[leftmargin=*, noitemsep, topsep=0.1em]

    \item Created Pinocchio, an autonomous puppet capable of emotional response and ethical reasoning.

    \item Developed innovative joint mechanisms for enhanced puppet mobility and expression.

    \item Mentored 15 apprentices in traditional woodcarving techniques and mechanical design.

\end{itemize}
\vspace{0.3em}


% Projects
\section*{Projects}

\textbf{\href{https://en.wikipedia.org/wiki/Pinocchio}{Pinocchio}}, \hfill Ongoing \\
A fully articulated wooden puppet designed for emotional expressiveness and narrative-constrained learning.
Combines handcrafted form with emergent behavioral systems and ethical instruction frameworks.
 \\
\vspace{0.3em}


% Education
\section*{Education}

\textbf{Guild of Master Carvers, } \hfill Florence, Italy \\
Journeyman Woodworker Certification, \hfill 1842
\vspace{0.3em}

\textbf{Independent Study, } \hfill Venice, Italy \\
Apprenticeship in Automata Construction and Puppet Mechanics, \hfill 1845
\vspace{0.3em}


% Honors and Awards
\section*{Honors and Awards}

\textbf{Best Toymaker in Tuscany,} \hfill December 1883 \\
Awarded by the Tuscany Chamber of Artisans for craftsmanship, community impact, and imaginative design.
\vspace{0.3em}


% Publications
\section*{Publications}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0.1em]

    \item \textit{\href{}{The Heart Inside the Wood: Designing for Growth}}. Preprint (submitted).

    \item \textit{\href{}{Whimsy and Will: Puppetry as a Medium for Ethical Development}}. Symposium Proceedings.

\end{itemize}

\end{document}